\documentclass{beamer}

\usetheme{Madrid}

\title{Research Progress}
\subtitle{What I learn from "Can AI Agents Agree?"}
\author{Chiharu Tomimori}
\date{\today}

\begin{document}

%------------------------------------------------
\begin{frame}
\titlepage
\end{frame}

%------------------------------------------------
\begin{frame}{Research Motivation}

\textbf{Question}

\vspace{0.3cm}

Can AI-agents reliably reach consensus like distributed systems?

\vspace{0.4cm}

\textbf{Focus of this report}

\begin{itemize}
    \item Compare \textbf{PBFT} and \textbf{Can AI Agents Agree?}
    \item Identify assumptions that no longer hold
    \item Explore possible research directions
\end{itemize}

\end{frame}

%------------------------------------------------
\begin{frame}{PBFT vs. AI-Agent Consensus}

\small

\begin{tabular}{p{4cm}p{3cm}p{4cm}}
\hline
 & PBFT & Can AI Agents Agree? \\
\hline
Node & Deterministic process & AI-Agent \\
Execution & Fixed protocol & Natural language reasoning \\
Failure Model & Byzantine node & Byzantine + reasoning errors \\
Output & Identical value & Probabilistic answer \\
Consensus Target & State / value & Answer agreement \\
\hline
\end{tabular}

\vspace{0.5cm}

\textbf{Key Difference}

PBFT assumes correct nodes always execute the protocol faithfully,
while AI-agents may misunderstand the protocol itself.

\end{frame}

%------------------------------------------------
\begin{frame}{Where PBFT Assumptions Break}

PBFT assumes:

\begin{itemize}
    \item Correct nodes always follow the protocol.
    \item Messages are interpreted correctly.
    \item State transitions are deterministic.
\end{itemize}

\vspace{0.4cm}

AI-agents introduce new uncertainties:

\begin{itemize}
    \item Hallucination
    \item Prompt misunderstanding
    \item Context forgetting
    \item Non-deterministic reasoning
\end{itemize}

\vspace{0.4cm}

These behaviors are not covered by the classical Byzantine fault model.

\end{frame}

%------------------------------------------------
\begin{frame}{Updated Research Direction}

\textbf{What I learned from this paper}

\begin{itemize}
    \item AI-agents are probabilistic protocol executors
    \item Even honest agents may fail to follow consensus protocols
    \item Evaluating AI-agent distributed systems is difficult
\end{itemize}

\vspace{0.4cm}

\textbf{Current decision}

\begin{itemize}
    \item Pause the AI-agent research direction
    \item Shift my focus to Kubernetes-based distributed systems
    \item Explore concrete research topics in the next step
\end{itemize}

\end{frame}

%------------------------------------------------
\begin{frame}{Takeaways}

\begin{itemize}
    \item PBFT and AI-agents have fundamentally different assumptions.
    \item Correct execution can no longer be assumed for AI-agents.
    \item Existing work studies answer consensus.
    \item Workflow consensus remains largely unexplored.
    \item Next step:
    \begin{itemize}
        \item Read the system model carefully.
        \item Analyze the failure assumptions.
        \item Compare with PBFT formally.
    \end{itemize}
\end{itemize}

\end{frame}

\end{document}