\documentclass[aspectratio=169]{beamer}

\usetheme{Madrid}
\usecolortheme{default}

\title{Research Progress}
\subtitle{Paxos Simulator and RAG Research Direction}
\author{Chiharu Tomimori}
\date{2026/7/6}

\begin{document}

% --------------------
% Title
% --------------------
\begin{frame}
  \titlepage
\end{frame}

% --------------------
% Slide 1
% --------------------
\begin{frame}{Presentation Overview}
  \begin{itemize}
    \item Today, I will explain two parts of my recent progress.
    \item First, I will explain my educational Paxos simulator.
    \item I refactored the simulator, added a simple network layer, and implemented failure scenarios.
    \item Second, I will explain my current research direction after reviewing recent RAG papers.
    \item The main goal is to connect my implementation practice with my broader research interest in distributed systems.
  \end{itemize}
\end{frame}

% --------------------
% Slide 2
% --------------------
\begin{frame}{Part 1: Educational Paxos Simulator}
  \begin{itemize}
    \item I extended the simulator beyond the basic Paxos flow.
    \item The goal is not to build a production-level Paxos system.
    \item Instead, the goal is to understand why Paxos needs:
    \begin{itemize}
      \item proposal numbers,
      \item Prepare / Promise,
      \item majority agreement,
      \item careful message handling.
    \end{itemize}
    \item I focused on making failure scenarios visible through code.
  \end{itemize}
\end{frame}

% --------------------
% Slide 3
% --------------------
\begin{frame}{Paxos Simulator: Main Updates}
  \begin{itemize}
    \item I made three main updates.
  \end{itemize}

  \vspace{0.5em}

  \begin{enumerate}
    \item Refactored \texttt{simulator.py}
    \item Added \texttt{network.py}
    \item Implemented failure scenarios
  \end{enumerate}

  \vspace{0.5em}

  \begin{block}{Main Goal}
    Understand why Paxos is designed this way by observing how it behaves under failure scenarios.
  \end{block}
\end{frame}

% --------------------
% Slide 4
% --------------------
\begin{frame}{Refactored Simulator}
  \begin{itemize}
    \item Before refactoring, \texttt{PaxosSimulator} handled most of the logic by itself.
    \item It created Prepare messages, collected Promise messages, selected values, created AcceptRequest messages, and collected Accepted responses.
    \item This worked, but it made the roles unclear.
    \item After refactoring, I separated the logic into three parts:
    \begin{itemize}
      \item \texttt{Proposer}: creates messages and stores responses.
      \item \texttt{Acceptor}: decides whether to promise or accept.
      \item \texttt{PaxosSimulator}: coordinates the overall protocol flow.
    \end{itemize}
  \end{itemize}
\end{frame}

% --------------------
% Slide 5
% --------------------
\begin{frame}{Why Refactoring Helps}
  \begin{itemize}
    \item Paxos has clear roles in theory.
    \item If all logic is inside the simulator, it becomes hard to see what each node does.
    \item After refactoring, each class has a specific responsibility.
    \item This also makes future extensions easier.
    \item For example, when I added \texttt{network.py}, the simulator did not need to contain all network-related logic.
  \end{itemize}

  \begin{block}{Key Idea}
    The simulator should control the flow, but the Paxos logic should belong to the nodes.
  \end{block}
\end{frame}

% --------------------
% Slide 6
% --------------------
\begin{frame}{Network Layer}
  \begin{itemize}
    \item I added \texttt{network.py} to simulate an unreliable network.
    \item It does not use real sockets or TCP.
    \item Instead, it manages messages inside the program.
    \item The main operations are:
    \begin{itemize}
      \item \texttt{send}
      \item \texttt{delay}
      \item \texttt{drop}
      \item \texttt{deliver\_one}
    \end{itemize}
    \item This allows me to explicitly control message delivery, delay, and loss.
  \end{itemize}
\end{frame}

% --------------------
% Slide 9
% --------------------
\begin{frame}{Leader Conflict Scenario}
  \begin{itemize}
    \item This scenario intentionally skips Prepare and Promise.
    \item P1 sends \texttt{AcceptRequest(1, A)} to A1 and A2.
    \item Since A1 and A2 form a majority, value A becomes chosen.
    \item Then P2 sends \texttt{AcceptRequest(2, B)} to A2 and A3.
    \item A2 and A3 also form a majority, so value B also becomes chosen.
    \item Now two different values are chosen for the same slot.
  \end{itemize}

  \begin{block}{Problem}
    This is a safety violation.
  \end{block}
\end{frame}

% --------------------
% Slide 10
% --------------------
\begin{frame}{Why Paxos Prevents Leader Conflict}
  \begin{itemize}
    \item In real Paxos, P2 cannot simply skip Prepare and send AcceptRequest.
    \item Before sending AcceptRequest, P2 must collect Promise messages.
    \item If an Acceptor has already accepted a value, it includes that value in its Promise.
    \item In the leader conflict example, A2 would tell P2 that value A was already accepted.
    \item Therefore, P2 must inherit A and send \texttt{AcceptRequest(2, A)}.
  \end{itemize}

  \begin{block}{Key Lesson}
    Prepare and Promise prevent a new leader from blindly overwriting a value that may already be chosen.
  \end{block}
\end{frame}

% --------------------
% Slide 11
% --------------------
\begin{frame}{What I Learned from the Simulator}
  \begin{itemize}
    \item Paxos safety depends on several mechanisms working together.
    \item Proposal numbers protect the system from old leaders and old messages.
    \item Majority agreement ensures that a value is chosen only when enough Acceptors accept it.
    \item Prepare and Promise allow a new Proposer to learn about previously accepted values.
    \item Refactoring helped me understand the roles more clearly.
    \item Network simulation made abstract failure cases much more concrete.
  \end{itemize}
\end{frame}

% --------------------
% Slide 13
% --------------------
\begin{frame}{Part 2: Why I Am Interested in RAG}
  \begin{itemize}
    \item I became interested in Retrieval-Augmented Generation, or RAG, through my previous university research.
    \item In that work, I studied how external knowledge can be used to improve the reliability of LLM outputs.
    \item However, this also means that RAG is not only an AI problem, but also a data management problem.
  \end{itemize}

  \begin{block}{Motivation}
    I want to study RAG from a distributed systems perspective.
  \end{block}
\end{frame}

% --------------------
% Slide 14
% --------------------
\begin{frame}{Main Question}
  \begin{block}{Main Research Question}
    How can we make RAG systems reliable when the knowledge base is dynamically updated?
  \end{block}

  \begin{itemize}
    \item In real systems, documents are not static.
    \item Documents can be added, updated, or deleted.
    \item These changes must be reflected in chunks, embeddings, vector indexes, retrieved contexts, and citations.
    \item If the propagation is incomplete, the LLM may generate answers based on stale or deleted information.
  \end{itemize}
\end{frame}

% --------------------
% Slide 15
% --------------------
\begin{frame}{Review Paper}
  \begin{block}{Reviewed Paper}
    \textit{Security and Privacy in Retrieval-Augmented Generation: Architectures, Threats, Defenses, and Future Directions for Building Trustworthy Systems}
  \end{block}

  \begin{itemize}
    \item This review paper surveys security and privacy issues in RAG systems.
    \item It shows that RAG introduces risks not only in the LLM, but also in retrieval, indexing, context construction, and generation.
    \item The paper helped me understand that trustworthy RAG requires system-level design.
    \item This motivated me to focus on reliability issues inside the RAG pipeline.
  \end{itemize}
\end{frame}

% --------------------
% Slide 16
% --------------------
\begin{frame}{Core Research Problem}
  \begin{block}{Problem}
    A RAG answer may be generated from outdated or inconsistent evidence.
  \end{block}

  \begin{center}
    \Large
    Document $\rightarrow$ Chunk $\rightarrow$ Embedding $\rightarrow$ Vector Index $\rightarrow$ Context $\rightarrow$ Answer
  \end{center}

  \vspace{0.8em}

  \begin{itemize}
    \item A document may be updated, but old chunks may remain.
    \item Embeddings may be generated from outdated text.
    \item Deleted documents may still exist in the vector index.
    \item Citations may point to old document versions.
  \end{itemize}
\end{frame}

% --------------------
% Slide 17
% --------------------
\begin{frame}{Why This Is a Distributed Systems Problem}
  \begin{itemize}
    \item Production RAG systems may use replicated or sharded vector indexes.
    \item Updates and deletions must propagate across multiple components.
    \item Queries may reach stale replicas or stale cached results.
    \item Different parts of the RAG pipeline may observe different versions of the knowledge base.
  \end{itemize}

  \begin{block}{Research Direction}
    I want to study consistency guarantees for dynamic RAG systems, especially freshness, deletion guarantees, and snapshot consistency.
  \end{block}
\end{frame}

% --------------------
% Slide 18
% --------------------
\begin{frame}{Overall Conclusion}
  \begin{itemize}
    \item Through the Paxos simulator, I learned how distributed protocols preserve safety under message delay and leader conflict.
    \item Through the RAG paper review, I found that RAG also has system-level reliability problems.
    \item My current research interest is to connect these two directions.
    \item I want to study RAG as a distributed data system where versioning, freshness, deletion, and consistency must be guaranteed.
  \end{itemize}
\end{frame}

\end{document}